---
title: "Week 3 Marriage Data Reflection Exercise"
subtitle: ""
author: 
  - Arav Sri Agarwal
thanks: "Code and data are available at: https://github.com/Aravsria/Week-3-Starter-Folder-Arav-Agarwal-Group-29.git"
date: "19 September 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```

# Introduction

This paper explores the use of R programming to analyze marriage license data from open.toronto.ca. 

# Data {#sec-mydatasection}

Our data is related to marriages (@fig-marriage).

```{r}
#| label: fig-marriage
#| fig-cap: Quantity of Marriage License vs Time
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Our data delivers insight into how the number of marriage licenses issued has varied with time


# Discussion

## First discussion point {#sec-first-point}

"The analysis reveals a significant rise in marriage licenses after the pandemic"

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps...

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


